---
title: "Correlated Categorical Data"
author: "Mohd Azmi"
date: "10/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(pacman)
p_load(aplore3, tidyverse, knitr, broom, summarytools, gee, lme4, sjPlot, HSAUR2, ggplot2)
```

```{r}
myds0 <- glow_rand
head(myds0)
```

```{r}
myds1 <- myds0 %>% 
  mutate(weight5 = weight/5,
         frac2 = as.numeric(fracture)-1)

freq(myds1$fracture)
descr(myds1$frac2)
```
# GEE model


```{r}
glow_gee <- gee(frac2 ~ weight5 + raterisk + armassist, id=site_id,
                data = myds1, family = binomial(), corstr = "independence", maxiter = 100)
glow_gee
```

```{r}
coef(glow_gee)
exp(coef(glow_gee))
```

# Conditional model - clustered specific

## random intercept

```{r}
glow_lme <- glmer(fracture ~ weight5 + raterisk + armassist + (1|site_id),
                  family = binomial, nAGQ = 20, data = myds1)
summary(glow_lme)
```

### fixed effect

```{r}
cbind(fixef(glow_lme), exp(fixef(glow_lme)))
```

### fixed effect CI

```{r}
glowlme_feci <- confint(glow_lme, parm = "beta_")

cbind(glowlme_feci, exp(glowlme_feci))
```

### Random Effect

```{r}
glowlme_ranef <- ranef(glow_lme)
glowlme_ranef
```

```{r}
glowlme_intercept <- data.frame(glowlme_ranef$site_id, cons = -.471, glowlme_ranef$site_id-.471)
colnames(glowlme_intercept) <- c("Random Effect", "Overall Intercept", "Predicted Intercept")
glowlme_intercept

```

### plot

```{r}
p_load(sjPlot)
#sjp.lmer(glow_lme, y.offset=0.5)
```

### Prediction

```{r}
glowlmw_predprob <- predict(glow_lme, type = "response")
head(glowlmw_predprob)
```


```{r}
glowlme_predlogodd <- augment(glow_lme) #same with predit (type=link)
head(glowlme_predlogodd)
```

## Level 2 predictor - SITE

```{r}
newds1 <- expand.grid(site_id = c(1:6),
                        armassist = c('Yes', 'No'),
                        raterisk = c('Less', 'Same', 'Greater'),
                        weight5 = mean(myds1$weight5))
newds1
```

```{r}
glowlme_newds_predlogodd <- augment(glow_lme, newdata = newds1) #same with predit (type=link)
glowlme_newds_predlogodd
```


```{r}
glowlme_newds_predprob <- predict(glow_lme, newdata = newds1, type = "response")
cbind(newds1, glowlme_newds_predprob, glowlme_newds_predlogodd$.fitted)
```

# Multilevel random intercept & random slope

```{r}
myds2 <- read.table("7.5.txt", header = TRUE, sep = ",")
head(myds2)
```

## Estimation

### multiple RI

```{r}
commglmermod0 <- glmer(antemed ~ magec + magecsq + meduc2 + meduc3 + wealthc + (1|comm), data = myds2, family = binomial())
summary(commglmermod0)
```

### RS for wealthc

```{r}
commglmermod0_RSwealth <- glmer(antemed ~ magec + magecsq + meduc2 + meduc3 + wealthc + (1+ wealthc|comm), data = myds2, family = binomial())
summary(commglmermod0_RSwealth)
```

### confirm RS for wealthc - by ANOVA

```{r}
anova(commglmermod0, commglmermod0_RSwealth)

```

# Model 2

```{r}
antemedglmer0_wealthRS <- glmer(antemed ~ mage + wealth + (1 + wealth| comm),
                       family = binomial, data = myds2)
summary(antemedglmer0_wealthRS)
```

## Prediction

```{r}
antemedglmer0_wealthRS_predlogodd <- augment(antemedglmer0_wealthRS)
antemedglmer0_wealthRS_predlogodd

```

# Longitudinal Data - toenail

```{r}
myds3 <- toenail
myds3
descr(myds3)
freq(myds3)
```

```{r}
ggplot(myds3, aes(visit)) +
  geom_bar(aes(fill=outcome)) +
  facet_grid(treatment~.) +
  scale_x_continuous(breaks = seq(0,8,1))
```
## GEE model - pop average model


```{r}
myds3_1 <- myds3 %>% 
  mutate(outcome2 = as.numeric(outcome)-1)
myds3_1

gee_toe <- gee(outcome2 ~ treatment + visit, id = patientID,
               data = myds3_1, family = binomial, corstr = "exchangeable", 
               scale.fix = T, scale.value = 1)
summary(gee_toe)
```

## Random Intercept

```{r}
glmertoe1 <- glmer(outcome ~ treatment*time + (1|patientID),
                   data = myds3, family=binomial, nAGQ = 20)
summary(glmertoe1)
```

### OR CI

```{r}
cbind(fixef(glmertoe1), exp(fixef(glmertoe1)))
```

```{r}
print(exp(cbind(est = fixef(glmertoe1), confint(glmertoe1, parm = "beta_"))), digits=3)
```

### Prediction