---
title: "Correlated Categorical Data"
author: "Mohd Azmi"
date: "10/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Environment

##Library

```{r}
library(pacman)
p_load(aplore3, tidyverse, knitr, broom, summarytools, gee, lme4, sjPlot, HSAUR2, ggplot2)
```


##Dataset
```{r}
myds0 <- glow_rand
myds0
```

refer Hosmer Applied Logistic Regression (3rd ed) - [page 324]

- 6 site
  - smallest no of subject - site 4 (24 subject)
  - largest no of subject - site 2 (113 subject)
- 124 physician - cluster size from 1 - 13 physician in various cluster
- (outcome) - fracture - occurence of fracture 

# Data Exploration

## No of groups

site id
```{r}
myds0 %>% count(site_id)
```

no of id for each site
```{r}
myds0 %>% count(site_id, phy_id)
```



## Data wrangling
```{r}
myds1 <- myds0 %>% 
  mutate(weight5 = weight/5,
         frac2 = as.numeric(fracture)-1)

freq(myds1$fracture)
descr(myds1$frac2)
```

# Revision - logistic regression

```{r}
glow_logreg <- glm(fracture ~ weight5 + raterisk + armassist, data = myds1, family = binomial())
summary(glow_logreg)
```

# Multilevel Random Intercept Model

## GEE model

```{r}
glow_gee <- gee(frac2 ~ weight5 + raterisk + armassist, id=site_id,
                data = myds1, family = binomial(), corstr = "independence", maxiter = 100)
glow_gee
```

```{r}
coef(glow_gee)
exp(coef(glow_gee))
```

## Conditional Model - Clustered Specific

### Random Intercept

```{r}
glow_lme <- glmer(fracture ~ weight5 + raterisk + armassist + (1|site_id),
                  family = binomial, nAGQ = 20, data = myds1)
summary(glow_lme)
```

```{r}
glow_lme_tidy<- tidy(glow_lme, conf.int=T, effects = "fixed")
glow_lme_tidy
```


## Fixed Effect

```{r}
cbind(fixef(glow_lme), exp(fixef(glow_lme)))
```

alternatively

```{r}
glow_lme_tidy %>% mutate(or = exp(estimate))
```


### fixed effect CI

```{r}
glowlme_feci <- confint(glow_lme, parm = "beta_")

cbind(glowlme_feci, exp(glowlme_feci))
```

alternatively

```{r}
glow_lme_tidy %>% mutate(or = exp(estimate),
                         lci = exp(conf.low),
                         uci = exp(conf.high))
```


## Random Effect

```{r}
glowlme_ranef <- ranef(glow_lme)
glowlme_ranef
```

```{r}
glowlme_intercept <- data.frame(glowlme_ranef$site_id, cons = -.471, glowlme_ranef$site_id-.471)
colnames(glowlme_intercept) <- c("Random Effect", "Overall Intercept", "Predicted Intercept")
glowlme_intercept

```

##Plot

###Fixed Effect

```{r}
plot_model(glow_lme, type = "est")
```

###Random Effect
```{r}
plot_model(glow_lme, type = "re")
```


## Prediction/estimation - Level 1 - Subject

### Predicted probability

```{r}
glowlmw_predprob <- predict(glow_lme, type = "response")
head(glowlmw_predprob, 10)
```

### Predicted logit

```{r}
glowlmw_predlogit <- predict(glow_lme, type = "link")
head(glowlmw_predlogit, 10)
```
alternatively

```{r}
glowlme_predlogodd <- augment(glow_lme) #same with predict (type=link)
head(glowlme_predlogodd)
```

### logit/logodd and probability relationship

probability = (odd a)/(1- odd a)

```{r}
head(exp(glowlmw_predlogit)/(1 + exp(glowlmw_predlogit)),10) #same with predict (type = "response")
```


## Level 2 predictor - SITE

```{r}
newds1 <- expand.grid(site_id = c(1:6),
                        armassist = c('Yes', 'No'),
                        raterisk = c('Less', 'Same', 'Greater'),
                        weight5 = mean(myds1$weight5))
newds1
```


### predict log odd for each site

```{r}
glowlme_newds_predlogodd <- augment(glow_lme, newdata = newds1) #same with predict (type=link)
glowlme_newds_predlogodd
```

### predict probability for each site

```{r}
glowlme_newds_predprob <- predict(glow_lme, newdata = newds1, type = "response")
newds1 %>% mutate("Predicted Probability" = glowlme_newds_predprob,
                  "Predicted Log Odds"= glowlme_newds_predlogodd$.fitted)
```



# Multilevel random intercept & random slope

```{r}
myds2 <- read.table("7.5.txt", header = TRUE, sep = ",")
myds2
```

from http://www.bristol.ac.uk/cmm/media/learning/lemma/7-r-sample.pdf

- comm = Community identifier
- womid = Woman identifier
- antemed = Received antenatal care at least once from a medically-trained provider, e.g. doctor, nurse or midwife (1=yes, 0=no)
- bord = Birth order of child (ranges from 1 to 13)
- mage = Mother’s age at the child’s birth (in years)
- urban = Type of region of residence at survey (1=urban, 0=rural)
- meduc = Mother’s  level  of  education  at  survey  (1=none,  2=primary,3=secondary or higher)
- islam = Mother’s religion (1=Islam, 0=other)
- wealth = Household wealth index in quintiles (1=poorest to 5=richest)

```{r}
myds2 %>% count(comm)
```


## Estimation

### multiple RI

```{r}
commglmermod0 <- glmer(antemed ~ magec + magecsq + meduc2 + meduc3 + wealthc + (1|comm),
                       data = myds2, family = binomial(),
                       glmerControl(calc.derivs = F))
summary(commglmermod0)
```

### RS for wealthc

```{r}
commglmermod0_RSwealth <- glmer(antemed ~ magec + magecsq + meduc2 + meduc3 + wealthc + (1+ wealthc|comm),
                                data = myds2, family = binomial(),
                                glmerControl(calc.derivs = F))
summary(commglmermod0_RSwealth)
```

### confirm RS for wealthc - by ANOVA

comparison using chi-square test --> which is wald test

```{r}
anova(commglmermod0, commglmermod0_RSwealth)
```

# Model 2

```{r}
antemedglmer0_wealthRS <- glmer(antemed ~ mage + wealth + (1 + wealth| comm),
                       family = binomial, data = myds2,
                       glmerControl(calc.derivs = F))
summary(antemedglmer0_wealthRS)
```

## Prediction

```{r}
antemedglmer0_wealthRS_predlogodd <- augment(antemedglmer0_wealthRS)
antemedglmer0_wealthRS_predlogodd

```

## Plot

### Fixed Effect Plot

```{r}
plot_model(antemedglmer0_wealthRS)
```

### Random Effect Plot

```{r}
plot_model(antemedglmer0_wealthRS, type = "re")
```

### Predict vs Marginal Effect plot

```{r}
plot_model(antemedglmer0_wealthRS, type = "pred", vars = "mage")
```



# Longitudinal Data - toenail

```{r}
myds3 <- toenail
myds3
descr(myds3)
freq(myds3)
```

```{r}
ggplot(myds3, aes(visit)) +
  geom_bar(aes(fill=outcome)) +
  facet_grid(treatment~.) +
  scale_x_continuous(breaks = seq(0,8,1))
```

## logistic regression model

```{r}
logreg_toe <- glm(outcome ~ treatment + visit,
                  data = myds3, family = binomial)
summary(logreg_toe)
```


## GEE model - pop average model

```{r}
myds3_1 <- myds3 %>% 
  mutate(outcome2 = as.numeric(outcome)-1)
myds3_1

gee_toe <- gee(outcome2 ~ treatment + visit, id = patientID,
               data = myds3_1, family = binomial, corstr = "exchangeable", 
               scale.fix = T, scale.value = 1)
summary(gee_toe)
```

## Random Intercept

```{r}
glmertoe1 <- glmer(outcome ~ treatment*time + (1|patientID),
                   data = myds3, family=binomial, nAGQ = 20)
summary(glmertoe1)
```

### OR CI

```{r}
cbind(fixef(glmertoe1), exp(fixef(glmertoe1)))
```

```{r}
print(exp(cbind(est = fixef(glmertoe1), confint(glmertoe1, parm = "beta_"))), digits=3)
```

### Prediction